Dirac neutrino mass generation from Majorana messenger

### 2019-08-06 draft.tex
lc

The mass matrix for Dirac neutrinos is diagonalized by
\begin{align}
(U^{(\nu)}_R)^{\dagger} \mathcal{M}_{\nu} U^{(\nu)}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
\end{align}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$  are unitary $3 \times 3$ matrices. In the most general Dirac neutrino mass matrices, lepton mixing matrix is
\begin{align}
U_{\text{PMNS}} = (U^{(\ell)}_L)^{\dagger} U^{(\nu)}_L\,.
\end{align}
If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstates, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$. Therefore, we can express the Dirac neutrino mass matrix in the following way
\begin{align}
(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.

>>>>

The mass matrix for Dirac neutrinos is diagonalized by
\begin{align}
(U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
\end{align}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are unitary $3 \times 3$
matrices. The leptonic charged currents with non-massless neutrinos
are parametrized in terms of the unitary mass
\begin{align}
U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
\end{align}
where is the left diagonalization matrix of the charged leptons.
As we already are in the diagonal basis after the calculation of the
one-loop neutrino masses, we can set
$U_{L}^{\ell} = \mathds{1}$. Moreover, we assume that $U_{R}^{\nu} = \mathds{1}$.
Therefore, we can express the Dirac neutrino mass matrix in the
following way
\begin{align}
(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.
